---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PolyMensa

<!-- badges: start -->
<!-- badges: end -->

PolyMensa is a small R package that scrapes the weekly menu of the
ETH Zurich Mensa Polyterrasse and helps users select a suitable meal
based on preferences such as day, meal time, dietary style, price, and
ingredients to avoid.

## Installation

You can install the development version of PolyMensa from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("macislover/PolyMensa")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(PolyMensa)
## basic example code

# fetch weekly menus
df_raw <- fetch_week(headless = TRUE)

# clean the menus
df_week <- clean_week(df_raw)

# select a menu

han_hunger(
  df_week,
  day = "Mi",
  time = "lunch",
  style = c("VEGAN, HOME"),
  avoid = c("Champignons"),
  max_price = 10
)

```

