---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PolyMensa

<!-- badges: start -->
<!-- badges: end -->

PolyMensa is a small R package that scrapes the weekly menu of the
ETH Zurich Mensa Polyterrasse and helps users select a suitable meal
based on preferences such as day, meal time, dietary style, price, and
ingredients to avoid.

## Installation

You can install the development version of PolyMensa from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("macislover/PolyMensa")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(PolyMensa)
## basic example code
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
